Case study: Genome-Wide Association Analyses (GWAS)

### 2018-05-14 datasets/GWAS/GWAS.Rmd
Compute stat from effect/SE instead of pval

```{r, GWAS1-reformat}
bmi <- bmi %>% 
    dplyr::rename(pval = p_value,
                  SE = stderr,
                  effect_size = effect,
                  ind_covar_N = N,
                  ind_covar_AF = Freq_Allele1_HapMapCEU) %>%
    mutate(test_statistic = qnorm(exp(log(pval)-log(2)), lower.tail=FALSE) * sign(effect_size)) %>%
    select(pval, SE, effect_size, ind_covar_N, ind_covar_AF, test_statistic) 
```

>>>>

```{r, GWAS1-reformat}
bmi <- bmi %>% 
    dplyr::rename(pval = p_value,
                  SE = stderr,
                  effect_size = effect,
                  ind_covar_N = N,
                  ind_covar_AF = Freq_Allele1_HapMapCEU) %>%
    mutate(test_statistic = effect_size / SE) %>%
    select(pval, SE, effect_size, ind_covar_N, ind_covar_AF, test_statistic) 
```
